Final Report

### 2022-05-09 Final Report.Rmd
first decade done

@@

#Joined all 
#X - year 
# Avg total deaths 
# color by continent 
```

>>>>

#High Population Deaths 1996 
p_high_first <- all_high_first %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= High_Deaths_96, fill = country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position = 'dodge')

interact_high_first<- p_high_first + labs(title="High Populated Countries", x="1996 Deaths")

#High Population Deaths 2001
p_high_first <- all_high_first %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= High_Deaths_01, fill = country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position = 'dodge')

interact_high_first<- p_high_first + labs(title="High Populated Countries", x="2001 Deaths")

#High Population Deaths 2006
p_high_first <- all_high_first %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= High_Deaths_06, fill = country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position = 'dodge')

interact_high_first<- p_high_first + labs(title="High Populated Countries", x="2006 Deaths")

@@

#Low Population Deaths 1996 
p_low_first <- all_low_first %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= Low_Deaths_96, fill = country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position = 'dodge')

interact_low_first<- p_low_first + labs(title="High Populated Countries", x="1996 Deaths")

#Low Population Deaths 2001 
p_low_first <- all_low_first %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= Low_Deaths_01, fill = country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position = 'dodge')

interact_low_first<- p_low_first + labs(title="High Populated Countries", x="1996 Deaths")

#Low Population Deaths 2006 
p_low_first <- all_low_first %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= Low_Deaths_06, fill = country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position = 'dodge')

interact_low_first<- p_low_first + labs(title="High Populated Countries", x="1996 Deaths")

ggplotly(interact_low_first)
```
